\documentclass[12pt]{article}
\usepackage{wasysym}
\usepackage{phonenumbers}
\usepackage{xcolor}
\usepackage[UKenglish]{isodate}% http://ctan.org/pkg/isodate
\usepackage[paperwidth=8.5in, paperheight=11in,margin=1.0in]{geometry} 
\usepackage[USenglish]{babel}
\usepackage{hyperref}
\usepackage[activate={true,nocompatibility},final,tracking=true,kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}
\frenchspacing
\usepackage[nodayofweek,level]{datetime}
\usepackage{calc,url}
\newcounter{qz}\setcounter{qz}{0}
\newcommand{\qz}{%\
\setcounter{qz}{\value{qz}+1}
\textbf{ICW  \theqz} \,\,}

\newcounter{hw}\setcounter{hw}{0}
\newcommand{\hw}{%\
\setcounter{hw}{\value{hw}+1}
\textbf{HW \thehw} \,\,}

\newcounter{ex}\setcounter{ex}{0}
\newcommand{\ex}{%\
\setcounter{ex}{\value{ex}+1}
Exam \theex}

\usepackage[T1]{fontenc} 
\usepackage{fourier}

\newenvironment{mypar}[2]
  {\begin{list}{}%
    {\setlength\leftmargin{#1}
    \setlength\rightmargin{#2}}
    \item[]}
  {\end{list}}


\newcounter{wk}\setcounter{wk}{0}
\newcommand{\wk}{%\
\setcounter{wk}{\value{wk}+1}
\thewk \,\,}

\newcommand{\term}{Fall }

\usepackage{enumerate}
\usepackage{graphicx}

\newenvironment{alphalist}{
  \begin{enumerate}[(a)]
    \addtolength{\itemsep}{-0.5\itemsep}}
  {\end{enumerate}}
  \cleanlookdateon% Remove ordinal day reference
  \newcommand{\RomanNumeralCaps}[1]
      {\MakeUppercase{\romannumeral #1}}

\newcommand{\coursename}{Calculus \RomanNumeralCaps{2} with Analytic Geometry}
\newcommand{\coursenumber}{MATH 202}
\newcommand{\sectionnumber}{01}

\begin{document}
\large
\begin{center}
    \textbf{\coursename}  \\
    {\coursenumber--\sectionnumber} \\
     {\term \the\year} \\
\end{center}

\vskip0.25in
\normalsize


\begin{center}
\begin{description}
    \item[Instructor:] Dr.\  Willis, Professor of Mathematics
    \item[Office:]  Discovery Hall,  Room 368
    \item[\phone:]  \phonenumber[country=US]{3088658868}
    \item[Email:] \href{mailto:willisb@unk.edu}{willisb@unk.edu}
    \item[Office Hours:] Either in person or by Zoom: Monday, Wednesday, and  Friday, \mbox{9:30 -- 11:00}; Tuesday and Thursday 13:00 -- 14:00; Monday and Wednesday 13:30 -- 15:00;  and by appointment.
    \item[Zoom] For both Zoom office hours or class meetings, use the \textbf{Meeting ID: 616 568 5706}.
 \end{description}
\end{center}

\subsubsection*{Course objectives}

Students will learn: applications of the antiderivative, methods for finding antiderivatives, the definitions and properties of the logarithm, exponential, and related functions,
the concepts, theorems, and proofs relating to sequences and infinite series, and the properties of the polar coordinate system.

\subsubsection*{Prerequisite}

To be in this class, you must have already earned a grade of D- or  greater  in  Calculus I (UNK's MATH 115).

\subsubsection*{Course Resources}

\begin{alphalist}

\item \emph{University Calculus: early transcendentals}, fourth edition (required), by Hass,  Heil, Weir, and Bogacki.

\item MyMathLab (required).  The Course ID is willis91782 

\item Reliable Internet access.

\item An Internet connected camera (for turning in class work electronically).

\item  An Internet connected computer (not just a phone or tablet) that can run Zoom. 

\item If we need to convert this class to remote learning, your computer will need to have a microphone and a camera. For remote office hours, it can be useful to have a separate camera that can be pointed toward a well-lit writing surface.

\item A basic scientific calculator (needn't be a graphing calculator).

\item Pencils, erasers, notebook for note taking. Colored pens or pencils are nice for note taking.

\end{alphalist}

\subsubsection*{Class meeting times}

Generally, this  class meets for 50 minutes Monday through Friday. 
Occasionally, to make up for a snow day or for days that I have to 
be absent,  we will meet for 75 minutes on 
either Tuesday or Thursday. Additionally we will meet for 
75 minutes for each mid-term exam. 

\subsubsection*{Grading}

Your course grade will be based on online homework, in class work, midterm exams, and a comprehensive 
final exam; specifically:
\begin{mypar}{0.25in}{0.25in}
    \textbf{Online homework} (31 five point assignments) \dotfill 155 (total)\\
    \textbf{In class work}  (12 ten point assignments)  \dotfill 120 (total) \\
    \textbf{Mid-term exams 1,2, and 3} (100 points each) \dotfill 300 (total)\\
    \textbf{Exam 4} \dotfill 50 (total)\\
    \textbf{Comprehensive Final exam} \dotfill 150 (total)\\
\end{mypar}
\noindent Your course grade will be based on the percent of the available 
points. Course letter grades will be based on a ten point scale. 
Except for the grade of A+, grades in the lower third of each decade 
will be a minus grade and grades in the upper third of each decade 
will be a plus grade. For example, the B- range is 
$[80, 83 + 1/3)$, and the B+ range is $[86 + 2/3, 90)$. To earn a 
grade of A+ requires a course average that exceeds 98\%.

\subsubsection*{In-class work \& online homework}

Except for examination days, we will do in class work for a portion 
of each class on Tuesday. In class work must be turned in 
electronically to Canvas (not emailed to me) by midnight the day we 
do it. Online homework is due each Friday at midnight. 

\subsubsection*{Online classes}

If you are ill, please let me know and join class via Zoom. But technology doesn't 
always work, sometimes I forget to click all the buttons to make it work,
and the readability of class materials over Zoom is sometimes poor. So if you 
join class regularly by Zoom, it's your choice, but I do not recommend it. 

\subsubsection* {Policies}

\begin{enumerate}

    \item For online homework, you may work in groups and you may 
    seek help from the Learning Commons. 

\item For examinations, you make use a teacher provided crib sheet, but no other 
tools. Using unauthorized materials while taking a test will earn you a failing 
course grade. 

    \item Generally, if you are ill or absent for any reason (including 
    athletics), you must turn in your in class work on time. Permission to
    turn in work late must be made in advance, otherwise late in class work 
    will count zero points.

    \item Generally,  if you are ill or absent for any reason (including 
    athletics), you must turn in your online homework on time. Permission to
    turn in work online homework late must be made in advance, otherwise it will
    count zero points.
 

\item During class time, please refrain from playing with electronic devices. If your 
device usage distracts your classmates, I will ask you to put it away. If it's my 
impression that you are often not paying attention in class, I reserve the right to 
decline to help you during office hours.

\item The final examination will be \emph{comprehensive} and it will be given during the time scheduled by the University. Except for \emph{extraordinary circumstances}
you must take the exam at this time.

\item Class cancellations due to weather or illness or other 
unplanned circumstances may require that we make minor adjustments
to the course calendar, exam dates, and due dates or specifics for 
course assessments.

 
\item If you have questions about how your work has been graded, make an appointment with me immediately.

\item All printed materials, in either paper or digital form, that I provide for you in this class, are for your own use. Re-posting or sharing these 
materials with other persons is prohibited. 

\item Please regularly check Canvas  to verify that your scores have been recorded correctly.  If I made a mistake in recording one of
your grades, I'll correct it provided you saved your paper.

\end{enumerate}

\subsubsection*{Examinations and Homework}

Follow these guidelines while taking an examination or writing a solution to a homework question.

\begin{enumerate}

\item The work you turn in is expected to be \emph{accurate, complete, concise, neat}, and \emph{well-organized}.  \emph{You will not earn
full credit on work that falls short of these expectations.}




\item While writing an examination, you may use a pencil, eraser, a scientific calculator, and a teacher provided crib sheet. If you are a non-native speaker of English,
you may use a \emph{paper} translation dictionary.  

\item  You may \emph{not} use a phone or other such device during an examination--this includes checking the time on a phone. Phones and all such devices must be turned off and be out of sight while taking an exam. 



\item For examinations, show your work.  No credit will be given for multi-step problems without the necessary work. Your solution must contain enough detail
so that I am convinced that you could correctly work any similar problem. Also erase or clearly mark any work you want me to ignore; otherwise,
I'll grade it.  

\end{enumerate}


\subsubsection*{Students with Disabilities or Those Who are Pregnant}

\paragraph{Students with Disabilities} It is the policy of the University of Nebraska 
at Kearney to provide flexible and individualized reasonable 
accommodation to students with documented disabilities. To receive 
accommodation services for a disability, students must be
registered with the UNK Disabilities Services for Students (DSS) 
office, 175 Memorial Student Affairs Building, 
\phonenumber[country=US]{3088658214} or 
by email \href{mailto:unkdso@unk.edu}{unkdso@unk.edu}

\paragraph{UNK Statement of Diversity \& Inclusion:} UNK stands in solidarity and unity with our students of color, our Latinx and international students, our LGBTQIA+ students and students from other marginalized groups in opposition to racism and prejudice in any form, wherever it may exist. It is the job of institutions of higher education, indeed their duty, to provide a haven for the safe and meaningful exchange of ideas and to support peaceful disagreement and discussion. In our classes, we strive to maintain a positive learning environment based upon open communication and mutual respect. UNK does not discriminate on the basis of race, color, national origin, age, religion, sex, gender, sexual orientation, disability or political affiliation. Respect for the diversity of our backgrounds and varied 
life experiences is essential to learning from our similarities as well as our differences. The following link provides resources and other information regarding D\&I: 
\url{https://www.unk.edu/about/equity-access-diversity.php}

\paragraph{Students Who are Pregnant} It is the policy of the University of Nebraska at Kearney to provide flexible and individualized reasonable accommodation to students who are pregnant. To receive accommodation services due to pregnancy, students must contact Cindy Ference in Student Health, 308-865-8219. The following link provides information for students and faculty regarding pregnancy rights.\footnote{\tiny  \url{http://www.nwlc.org/resource/pregnant-and-parenting-students-rights-faqs-college-and-graduate-students}}

\paragraph{Reporting Student Sexual Harassment, Sexual Violence or Sexual Assault} Reporting allegations of rape, domestic violence, dating violence, sexual assault, sexual harassment, and stalking enables the University to promptly provide support to the impacted student(s), and to take appropriate action to prevent a recurrence of such sexual misconduct and protect the campus community. Confidentiality will be respected to the greatest degree possible. Any student who believes she or he may be the victim of sexual misconduct is encouraged to report to one or more of the following resources:
\begin{alphalist}
\item Local Domestic Violence, Sexual Assault Advocacy Agency \phonenumber[country=US]{3082372599}

\item Campus Police (or Security) \phonenumber[country=US]{3088658911}

\item Title \RomanNumeralCaps{9} Coordinator \phonenumber[country=US]{3088658655}

\end{alphalist}
Retaliation against the student making the report, whether by students or University employees, will not be tolerated.If you have questions regarding the information in this email please 
contact Mary Chinnock Petroski, Chief Compliance Officer (
   \href{mailto:petroskimj@unk.edu}{petroskimj@unk.edu} 
    or phone \phonenumber[country=US]{3088658400}.



\subsubsection*{Course Calendar}

Generally, we'll adhere to the scheduled exam dates even if we are ahead or behind with course work.  When we are ahead or behind, the
topics on the exams will be appropriately adjusted.  There is no new topics scheduled for dead week, if we adhere to the schedule, we'll review during dead week, but
if we fall behind, we'll cover new topics during dead week.

\noindent \textbf{Notices:}


\begin{alphalist}
   \item Exams will be given on the Tuesday of the week they are assigned.
   
   \item In class work (labeled \textbf{ICW}) will generally be 
    done on Tuesday of the week they are assigned.

    \item Online homework (labeled \textbf{HW}) will be due at midnight on
          Friday of the week they are assigned. 

    \item The homework assignment that is due the Friday after Thanksgiving
          will be assigned sufficiently early for you to complete it before
          the Thanksgiving break.
\end{alphalist}

\vspace{0.1in}

\center
    \small
\begin{tabular}  {|l|l|l|l|}
\hline
{\bf Week}  & \textbf{Monday} &  {\bf Section(s)} & {\bf Topic(s) \& Assessments} \\
\hline \hline 
\wk    & 8/23 &    \S6.1 -- \S6.3   & volumes using cross-sections and shells, arclength, \hfill \qz  \\
\wk    & 8/30  &  \S6.4 -- \S6.5   &  areas and work  \hfill \qz \hw  \\
\wk    & 9/6 &     \S6.6 --\S7.1  &  center of mass and logarithms \hfill \qz \hw \\
\wk    & 9/13  &     \S7.2 -- \S7.3  & separable DEs   and hyperbolic functions  \hfill \qz \hw            \\
\wk    & 9/20 &  \S8.1--\S8.2    &  integration by parts and trigonometric integrals    \hfill \textbf{\ex} \hw \\ \hline
\wk    & 9/27   & \S8.3 -- \S8.5   & trigonometric substitutions, rational functions, tables  \hfill \qz \hw  \\
\wk    & 10/4     & \S8.6 -- \S8.7  & numerical integration and improper integrals  \hfill \qz \hw  \\
\wk   & 10/11   & \S9.1 -- \S9.2  &   sequences, infinite series  \hfill \qz \hw  \\
\wk  &  10/18   & \S9.3 -- \S9.4 &  integral test, comparison   \hfill \qz  \hw \\ 
\wk &  10/25     &   \S9.5 -- \S9.6 &  absolute convergence, alternating series \hfill  \textbf{ \ex}  \hw \\ \hline
\wk  & 11/1  &   \S9.7 --\S9.8 & Power series, Taylor series \hfill \qz  \hw  \\
\wk   & 11/8  & \S9.9--\S9.10  &  Taylor series \hfill \qz \hw \\
\wk   & 11/15& \S10.1  -- \S10.2   & plane curves, calculus with plain curves   \hfill \qz \hw  \\
\wk   & 11/22   &  \S10.3 -- \S10.4   & polar coordinates, polar equations  \hfill \qz \hw  \\
\wk   & 11/29    &  \S10.5     &  area and length in polar coordinates  \hfill \textbf{ \ex}  \hw \\ \hline
\wk   & 12/6      &         &  catch up or review  \\  
\wk   & 12/13      &  &     \hfill \textbf{\ex,  13 December, 13:00--15:00} \\ 
         &               & &   \hfill  \textbf{ Final Exam, 16 December  10:30 -- 12:30} \\ \hline
\end{tabular}




\end{document}

\small
\begin{center}
\begin{tabular}{| l | l| l | l | l |}
\hline \textbf{Week} & \textbf{Class} & \textbf{Date} & \textbf{Section(s)} & \textbf{Homework assignment} \\
\hline \hline
%1
\wk & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  &  & introduction  \\ \hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & & introduction   \\ \hline  \setcounter{cd}{\value{cd}+1} 
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S5.4 &  1, 3, 4, 7, 8, 10, 13, 15 \\ 
           \hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S5.4 &  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S5.5 &  1--3,  9--12 \qz  \\ 
\hline \hline \setcounter{cd}{\value{cd}+3}

%2
\wk &     & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  &  &  no class  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S5.5 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1} 
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S5.6 & 8--18   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S5.6 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S5.7 & 1--12,  20, 21, 25, 26, 35 \qz  \\ 
\hline \hline \setcounter{cd}{\value{cd}+3}

%3
\wk & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.1  & 3--11, 15--26, 27--30, 47, 49, 50, 51\\
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.1 & \\ 
\hline  \setcounter{cd}{\value{cd}+1} 
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.2 & 7--8, 15--20, 44, 45  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.2 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.3 & 3--20, 25--32, 37--42 \qz   \\ \hline \hline 
          \setcounter{cmon}{\value{cmon}+1} \setcounter{cd}{1}
%4
\wk & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.3 &   \\ \hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.4 &  13--16, 17--26, 27--32, 35--39 \\ 
\hline  \setcounter{cd}{\value{cd}+1} 
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.4 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.5 & 1--4, 5--11, 17  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S5.4--\S6.4 & \ex  \\ 
\hline \hline \setcounter{cd}{\value{cd}+3}

%5
\wk & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.5 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.6 & 1--8, 15--17  \\ 
\hline  \setcounter{cd}{\value{cd}+1} 
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.6 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.8 & 1--10, 29--32, 33--36, 55--60  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.8 &  \qz \\ 
\hline \hline  \setcounter{cd}{\value{cd}+3} 

%6
\wk    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.9 & 1--8, 20--28, 38--42, 46--48  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.9 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S7.1 &  1--25 \\ 
\hline \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S7.1 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S7.2 & 1--26, 37--46, 49--51, 78  \qz \\ 
\hline  \hline \setcounter{cd}{\value{cd}+3} 

%7
\wk    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S7.2 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S7.3 &  1--28 \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S7.3 &  \\ 
\hline \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S7.4 & 1--10, 17--20  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S7.4 &    \qz \\ 
\hline \hline  \setcounter{cd}{1} \setcounter{cmon}{3} 

%8
\wk  & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S7.5 & 1--28, 41, 42  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S7.5 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S7.6 & 13--20  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S7.6 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S6.5--\S7.6 & \ex \\ 

\hline  \hline 
\end{tabular}
\setcounter{cd}{\value{cd}+3} 
\end{center}


\begin{center}
\begin{tabular}{| l | l| l | l | l |}
\hline \textbf{Week} & \textbf{Class} & \textbf{Date} & \textbf{Section(s)} & \textbf{Homework assignment} \\
\hline \hline

%9
\wk    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S8.1 & 1--20, 34--37  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S8.1 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S8.2&  1--28, 42 \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S8.2 & \\ 
\hline  \setcounter{cd}{\value{cd}+1}
   & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S8.3 & 1--20, 31--35  \qz \\ 

\hline \hline \setcounter{cd}{\value{cd}+10}
%10
\wk & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S8.3 &  \\ 
\hline  \setcounter{cd}{\value{cd}+1}

    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S8.4 & 1--28  \\ \hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S8.4 &   \\ \hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.1 & 1--10, 31--36, 37, 43, 44  \\ 
\hline \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.1   &  \qz \\ 
\hline  \hline \setcounter{cd}{\value{cd}+3}

\wk    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.2 & 1--14, 15--16, 21--24  \\ 
\hline  \setcounter{cd}{\value{cd}+1} 
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.2 &   \\ 
\hline  \setcounter{cd}{1} \setcounter{cmon}{4}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.3 & 1--6, 13--22, 23--26, 27--28  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.3 &  \\ 
\hline \setcounter{cd}{\value{cd}+1}
  & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.4 & 1--10, 11--19, 27--30 \qz  \\ 
\hline \hline \setcounter{cd}{\value{cd}+3}
\wk    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.4 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1} 
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.5 & 1--6, 7--12, 13--20   \\ 
\hline  \setcounter{cd}{\value{cd}+1} 
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.5 &  \\ 
\hline  \setcounter{cd}{\value{cd}+1} 
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.6 & 1--8, 9--16  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S7.7--\S9.5 &   \ex \\ 
\hline \hline \setcounter{cd}{\value{cd}+3}
%13
\wk & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.7 & 1--4, 11, 12, 13--16, 17, 18  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.8 & 1--4, 7, 27, 28, 29, 30  \\ 
\hline  \setcounter{cd}{\value{cd}+1} 
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.8 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.9 &  1--4, 19--22 \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S9.9 & 1--8 \qz \\ 
\hline \hline \setcounter{cd}{\value{cd}+3}
%14
\wk & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S10.1 &1--8, 9--14   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
      & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S10.2 & 1--6  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
     & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S10.3 &  1--4, 43--46  \\ 
\hline \setcounter{cd}{\value{cd}+1}
     & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S10.3 &   \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S10.4 & 1--4, 21--24 \qz  \\ 
\hline \hline  \setcounter{cd}{\value{cd}+3} 

\wk    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S10.4 &  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S10.5 & 1--2, 10, 11--16, 23--28  \\ 
\hline  \setcounter{cd}{\value{cd}+1}
  & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S10.6 &1--8   \\ \hline  \setcounter{cd}{\value{cd}+1}
     & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S10.7 &1--10   \\ \hline  \setcounter{cd}{\value{cd}+1}
 
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  &  &  \qz \\ \hline \hline 
\setcounter{cd}{4} \setcounter{cmon}{5}

\wk & & \formatdate{4}{5}{\value{cy}}  &\S 9.6--\S10.7  & 10:30  \ex  \\ \hline 
    & & \formatdate{5}{5}{\value{cy}}  & \S5.4--\S10.7 & 10:30  \hfill \textbf{Final \,\,} \\ \hline  %\setcounter{cd}{\value{cd}+1} 
\end{tabular}
\end{center}
\end{document}

%15
\wk & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S &   \\ \hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S &   \\ \hline  \setcounter{cd}{\value{cd}+1} 
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S &   \\ \hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S &   \\ \hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S &  \qz \\ \hline \hline \setcounter{cd}{\value{cd}+1}

\wk & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S &   \\ \hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S &   \\ \hline  \setcounter{cd}{\value{cd}+1} 
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S &   \\ \hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S &   \\ \hline  \setcounter{cd}{\value{cd}+1}
    & \dy & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  & \S &  \qz \\ \hline \hline 
\setcounter{cd}{4} \setcounter{cmon}{5}

\wk & & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  &  &  \ex  \\ \hline  \setcounter{cd}{\value{cd}+1}
    & & \formatdate{\value{cd}}{\value{cmon}}{\value{cy}}  &  &   \\ \hline  %\setcounter{cd}{\value{cd}+1} 
\end{tabular}
\end{center}
\end{document}


\wk & \dy & Mon & 28 &     \S6.2    &  11--18  \\ \hline
  & \dy & Tue & 29 & \S6.3  & 5--11, 21--24 \\ \hline
  & \dy & Wed & 30  & \S6.4  &  3--6 \\ \hline
  & \dy & Thu & 31  & \S6.5  & 1--4,\,\, 9,\,\,10,\,\,21,\,\,23 \hfill {\bf Quiz \qz} \\ \hline\hline 

\wk & \dy  & Mon & 4 Sept &  &  \hfill {\bf Vacation} \\ \hline
  & \dy & Tue & 5    & \S6.6  &   13--18,\,\, 25--28 \\ \hline
  & \dy & Wed & 6    & \S6.6  & 25--28 \\ \hline
  & \dy & Thu & 7   & \S6.7  & 5--10\hfill {\bf Quiz \qz}  \\ \hline \hline

\wk & \dy & Mon & 11  & \S6.7  & 20--22 \\ \hline
  & \dy & Tue & 12    & \S7.1 & 5--24,\,\, 63--66 \\ \hline
  & \dy & Wed & 13      & \S7.2 & 11--25 \\ \hline 
  & \dy & Thu & 14     & \S7.2 & 26--42 \hfill{\bf Quiz \qz} \\ \hline \hline

\wk  & \dy & Mon & 18      & \S7.3 & 3--8, 17--18 \\ \hline 
  & \dy& Tue &19& \S7.4& 17--24\\ \hline 
  & \dy& Wed &20& \S7.4& 25--32  \\ \hline 
 & \dy& Thu &21& \S7.5   & 7--14 \hfill {\bf Quiz \qz} \\ \hline \hline

\wk & \dy& Mon &25& \S7.5   & 15--24     \\ \hline
 & \dy  & Tue &26  & \S7.6   & 19--30  \hfill {\bf Quiz \qz}  \\ \hline 
 & \dy  & Wed &27  & \S7.7   & 5--30\\ \hline
 & \dy  & Thu &28  &    &    \hfill {\bf Exam \ex}  \\ \hline \hline

\wk & \dy  & Mon & 2 Oct.  & \S7.8   & 7--16   \\ \hline
 & \dy & Tue & 3   & \S7.8   & 17--26  \\ \hline 
 & \dy  & Wed & 4 & \S8.1   & 1--5, 13, 14, 31--36   \\ \hline
 & \dy  & Thu & 5 & \S8.1   & 47--58    \hfill  {\bf Quiz \qz}  \\ \hline \hline 

\wk & \dy & Mon & 9 Oct. & \S8.2   & 17--20, 21--26  \\ \hline
 & \dy  & Tue & 10 & \S8.2   & 27--32, 33--36   \\ \hline
 & \dy  & Wed & 11 & \S8.3   & 1--4, 13, 14,19,20   \\ \hline
 & \dy  & Thu & 12 & \S8.3   &   28, 35, 37--39  \hfill {\bf Quiz \qz}  \\
\hline\hline

\end{tabular}
\end{center}
\newpage

\begin{center}
\begin{tabular}{|l |l | l | l | l | l |} 
\hline {\bf  Week} & & {\bf Day} & {\bf Date} & {\bf Section} & {\bf Homework assignment} \\
\hline \hline
\wk &   & Mon & 16 &  & \hfill {\bf Vacation} \\ \hline
 &   & Tue & 17 &  & \hfill {\bf Vacation} \\ \hline
 & \dy  & Wed &18  & \S8.4   & 3--10   \\ \hline
 & \dy  & Thu &19  & \S8.4   & 15--22 \hfill {\bf Quiz \qz} \\ \hline \hline

\wk & \dy  & Mon &23  & \S8.5   & 9--16, 29--32  \\ \hline
 & \dy & Tue & 24 &\S8.5    & 33--36  \\ \hline
 & \dy & Wed &25  & \S8.6   & 13--20   \\ \hline
 & \dy  & Thu &26  & \S8.6   & 23--28, 33--34, 43--50 \hfill {\bf Quiz \qz} \\ \hline \hline

\wk & \dy  & Mon &30  & \S8.7   & 13--18, 33  \\ \hline
 & \dy  & Tue &31  & \S8.7   & 41--42   \hfill {\bf Quiz \qz} \\ \hline
 & \dy  & Wed &1 Nov.  & \S8.8   & 11--28   \\ \hline
 & \dy  & Thu &2  &         & \hfill {\bf Exam \ex} \\ \hline \hline

\wk & \dy  & Mon &6  & \S8.8   & 39--42, 47--49, 51 \\ \hline
 &  \dy & Tue &7  & \S8.8   & 47--49, 51  \\ \hline
 & \dy  & Wed & 8   & \S8.9   & 17--19, 36, 37   \\ \hline
 & \dy  & Thu & 9      & \S8.9   & 39, 41, 42--46 \hfill{ \bf Quiz \qz} \\
\hline \hline

\wk & \dy  & Mon & 13 & \S8.10   & 1--4, 13,14,21,22  \\ \hline
 & \dy  & Tue & 14 & \S8.10   & 45--48  \\ \hline
 & \dy  & Wed & 15& \S8.10   & 53--58 \\ \hline
 & \dy & Thu & 16& \S9.1   & 1--8, 9--16 \hfill{\bf Quiz \qz} \\ \hline \hline 

\wk & \dy  & Mon & 20& \S9.2   & 3--12   \\ \hline
 & \dy  & Tue & 21& \S9.2   & 21--24, 39--42, 48, 49  \hfill {\bf Quiz \qz} \\ \hline
 & \dy  & Wed & 22 &         & \hfill {\bf Vacation} \\ \hline
 & \dy  & Thu & 23 &         & \hfill {\bf Vacation} \\ \hline \hline

\wk  &\dy   & Mon & 27 & \S9.3   & 1--10   \\ \hline
 & \dy  & Tue & 28 & \S9.3   & 15,16, 25--30  \hfill {\bf Quiz \qz} \\ \hline 
 & \dy  & Wed & 29 & \S9.4   &1--6, 21--26   \\ \hline
 & \dy  & Thu & 30 & \S9.4   & 29--36 \hfill {\bf Exam \ex} \\ \hline \hline

\wk  & \dy  & Mon & 4 Dec &  \S9.5   & 9--14   \\   \hline
 &\dy   & Tue & 5 & \S9.5   & 24, 27, 30, 33 \\ \hline
 & \dy & Wed & 6 Dec.  & \S9.6   & 13--16, 27,28  \\ \hline
 &\dy   & Thu & 7 &   &    \\ \hline \hline

\wk &\dy &  Mon  & 11  &  &  \textbf{Comprehensive Final Exam 13:00--15:00} \\ \hline
\end{tabular}
\end{center}

\vfill

\copyright 2010 Barton Willis
\end{document}

\end{document}
\formatdate{1}{11}{2009}

\monthname[6]
\shortdayofweekname{31}{10}{2002}
\begin{center}
\begin{tabular}{| l |l | l | l | l | l |}
\hline \textbf{Week} & & {\bf Day} & {\bf Date} & {\bf Section} & {\bf Homework assignment} \\
\hline \hline
1 & 1 & Mon & 21 Aug.  &        &  Introduction to MATH 202 \\ \hline
  & 2 & Tue & 22       & \S5.10 & 7--12, 15--20, 33,34, 39--45 \\ \hline
  & 3 & Wed & 23       & \S5.10 & 55--62, 67--78 \\ \hline
  & 4 & Thu & 24       & \S6.1  &  15--25, 53--55 \hfill {\bf Quiz \qz} \\ \hline \hline


2 & 5 & Mon & 28 &     \S6.2    &  11--18  \\ \hline
  & 6 & Tue & 29 & \S6.3  & 5--11, 21--24 \\ \hline
  & 7 & Wed & 30  & \S6.4  &  3--6 \\ \hline
  & 8 & Thu & 31  & \S6.5  & 1--4,\,\, 9,\,\,10,\,\,21,\,\,23 \hfill {\bf Quiz \qz} \\ \hline\hline 

3 &   & Mon & 4 Sept &  &  \hfill {\bf Vacation} \\ \hline
  & 9 & Tue & 5    & \S6.6  &   13--18,\,\, 25--28 \\ \hline
  & 10& Wed & 6    & \S6.6  & 25--28 \\ \hline
  & 11 & Thu & 7   & \S6.7  & 5--10\hfill {\bf Quiz \qz}  \\ \hline \hline

4 & 12 & Mon & 11  & \S6.7  & 20--22 \\ \hline
  & 13 & Tue & 12    & \S7.1 & 5--24,\,\, 63--66 \\ \hline
  & 14 & Wed & 13      & \S7.2 & 11--25 \\ \hline 
  & 15& Thu & 14     & \S7.2 & 26--42 \hfill{\bf Quiz \qz} \\ \hline \hline

5  & 16& Mon & 18      & \S7.3 & 3--8, 17--18 \\ \hline 
  & 17& Tue &19& \S7.4& 17--24\\ \hline 
  & 18& Wed &20& \S7.4& 25--32  \\ \hline 
 & 19 & Thu &21& \S7.5   & 7--14 \hfill {\bf Quiz \qz} \\ \hline \hline

6 & 20& Mon &25& \S7.5   & 15--24     \\ \hline
 & 21  & Tue &26  & \S7.6   & 19--30  \hfill {\bf Quiz \qz}  \\ \hline 
 & 22  & Wed &27  & \S7.7   & 5--30\\ \hline
 & 23  & Thu &28  &    &    \hfill {\bf Exam \ex}  \\ \hline \hline

7& 24  & Mon & 2 Oct.  & \S7.8   & 7--16   \\ \hline
 & 25  & Tue & 3   & \S7.8   & 17--26  \\ \hline 
 & 26  & Wed & 4 & \S8.1   & 1--5, 13, 14, 31--36   \\ \hline
 & 27  & Thu & 5 & \S8.1   & 47--58    \hfill  {\bf Quiz \qz}  \\ \hline \hline 

8 & 28  & Mon & 9 Oct. & \S8.2   & 17--20, 21--26  \\ \hline
 & 29  & Tue & 10 & \S8.2   & 27--32, 33--36   \\ \hline
 & 30  & Wed & 11 & \S8.3   & 1--4, 13, 14,19,20   \\ \hline
 & 31  & Thu & 12 & \S8.3   &   28, 35, 37--39  \hfill {\bf Quiz \qz}  \\
\hline\hline

\end{tabular}
\end{center}
\newpage

\begin{center}
\begin{tabular}{|l |l | l | l | l | l |} 
\hline {\bf  Week} & & {\bf Day} & {\bf Date} & {\bf Section} & {\bf Homework assignment} \\
\hline \hline
9 &   & Mon & 16 &  & \hfill {\bf Vacation} \\ \hline
 &   & Tue & 17 &  & \hfill {\bf Vacation} \\ \hline
 & 32  & Wed &18  & \S8.4   & 3--10   \\ \hline
 & 33  & Thu &19  & \S8.4   & 15--22 \hfill {\bf Quiz \qz} \\ \hline \hline

10 & 34  & Mon &23  & \S8.5   & 9--16, 29--32  \\ \hline
 & 35  & Tue & 24 &\S8.5    & 33--36  \\ \hline
 & 36  & Wed &25  & \S8.6   & 13--20   \\ \hline
 & 37  & Thu &26  & \S8.6   & 23--28, 33--34, 43--50 \hfill {\bf Quiz \qz} \\ \hline \hline

11 & 38  & Mon &30  & \S8.7   & 13--18, 33  \\ \hline
 & 39  & Tue &31  & \S8.7   & 41--42   \hfill {\bf Quiz \qz} \\ \hline
 & 40  & Wed &1 Nov.  & \S8.8   & 11--28   \\ \hline
 & 41  & Thu &2  &         & \hfill {\bf Exam \ex} \\ \hline \hline

12 & 42  & Mon &6  & \S8.8   & 39--42, 47--49, 51 \\ \hline
 & 43  & Tue &7  & \S8.8   & 47--49, 51  \\ \hline
 & 44  & Wed & 8   & \S8.9   & 17--19, 36, 37   \\ \hline
 & 45  & Thu & 9      & \S8.9   & 39, 41, 42--46 \hfill{ \bf Quiz \qz} \\
\hline \hline

13 & 46  & Mon & 13 & \S8.10   & 1--4, 13,14,21,22  \\ \hline
 & 47  & Tue & 14 & \S8.10   & 45--48  \\ \hline
 & 48  & Wed & 15& \S8.10   & 53--58 \\ \hline
 & 49  & Thu & 16& \S9.1   & 1--8, 9--16 \hfill{\bf Quiz \qz} \\ \hline \hline 

14 & 50  & Mon & 20& \S9.2   & 3--12   \\ \hline
 & 51  & Tue & 21& \S9.2   & 21--24, 39--42, 48, 49  \hfill {\bf Quiz \qz} \\ \hline
 &   & Wed & 22 &         & \hfill {\bf Vacation} \\ \hline
 &   & Thu & 23 &         & \hfill {\bf Vacation} \\ \hline \hline

15 & 52  & Mon & 27 & \S9.3   & 1--10   \\ \hline
 & 53  & Tue & 28 & \S9.3   & 15,16, 25--30  \hfill {\bf Quiz \qz} \\ \hline 
 & 54  & Wed & 29 & \S9.4   &1--6, 21--26   \\ \hline
 & 55  & Thu & 30 & \S9.4   & 29--36 \hfill {\bf Exam \ex} \\ \hline \hline

16 & 56  & Mon & 4 Dec &  \S9.5   & 9--14   \\   \hline
 & 57  & Tue & 5 & \S9.5   & 24, 27, 30, 33 \\ \hline
 & 58  & Wed & 6 Dec.  & \S9.6   & 13--16, 27,28  \\ \hline
 & 59  & Thu & 7 &   &    \\ \hline \hline

 & &  Mon  & 11  &  &  \textbf{Comprehensive Final Exam 13:00--15:00} \\ \hline
\end{tabular}
\end{center}

\vfill

\copyright 2006 Barton Willis
\end{document}


7 & Thu & 4 Sept  & \S2.2  &   Basic Differentiation Rules, {\bf Quiz \qz} \\
 & & & & \quad     1-3, 6-51 (divisible by 3)\\\cline{1-5}

 & Mon & 6 Sept &  & {\bf Vacation} \\
 & & & & \quad  Study \S1.1-\S2.3 \\\cline{1-5}

8 & Mon & 8 & \S2.3  &   The Product and Quotient Rules \\
 & & & & \quad     3-48 (divisible by 3) \\\cline{1-5}

9 & Tue & 9 & \S2.4  &   The Chain Rule \\
 & & & & \quad      3-27 (divisible by 3)\\\cline{1-5}

10 & Wed & 10& \S2.4  &   The Chain Rule \\
 & & & & \quad     33-66 (divisible by 3)\\\cline{1-5}

11 & Thu & 11 & \S2.5  &   Implicit Differentiation, {\bf Quiz \qz} \\
 & & & & \quad     3-30 (divisible by 3) \\\cline{1-5}

12 & Mon & 15 &   &    {\bf Review} \\
 & & & & \quad    Study \S1.1-\S2.5\\\cline{1-5}

13 & Tue & 16 &  & {\bf Examination \ex} \\
 & & & & \quad    \S1.1-\S2.5\\\cline{1-5}

14 & Wed & 17 & \S2.6  &   Related Rates \\
 & & & & \quad     3-15 (divisible by 3)\\\cline{1-5}

15 & Thu & 18 & \S2.6  &   Related Rates, {\bf Quiz \qz} \\
 & & & & \quad     18-24 (divisible by 3)\\\cline{1-5}

16 & Mon & 22 & \S3.1  &   Extrema on an Interval \\
 & & & & \quad     3-33 (divisible by 3)\\\cline{1-5}

17 & Tue & 23 & \S3.2  &   Rolle's Theorem and the Mean Value Theorem \\
 & & & & \quad     3-24 (divisible by 3)\\\cline{1-5}

\hline
\end{tabular}
\end{center}
\newpage
\begin{center}
\begin{tabular}{|l | l | l | l | l |}
\hline & {\bf Day} & {\bf Date} & {\bf Section} & {\bf Topic(s) and Homework} \\
\hline \hline
18 & Wed & 24 & \S3.3  &   Increasing and Decreasing Functions \\
 & & & & \quad     3-48 (divisible by 3)\\\cline{1-5}

19 & Thu & 25 & \S3.4  &   Concavity and the Second Derivative Test, {\bf Quiz \qz} \\
 & & & & \quad     3-51 (divisible by 3)\\\cline{1-5}

20 & Mon & 29 & \S3.5  &   Limits at Infinity \\
 & & & & \quad     3-30 (divisible by 3)\\\cline{1-5}

21 & Tue & 30 & \S3.6  &   A Summary of Curve Sketching \\
 & & & & \quad     1-5\\\cline{1-5}

22 & Wed & 1 Oct & \S3.7  &   Optimization Problems \\
 & & & & \quad      3-15 (divisible by 3)\\\cline{1-5}

23 & Thu & 2 & \S3.7  &   Optimization Problems, {\bf Quiz \qz} \\
 & & & & \quad     21-30 (divisible by 3) \\\cline{1-5}

24 & Mon & 6 Oct  & \S3.8  &   Newton's Method \\
 & & & & \quad     1-6\\\cline{1-5}

25 & Tue & 7 & \S3.9  &   Differentials \\
 & & & & \quad     3-24 (divisible by 3) \\\cline{1-5}

26 & Wed & 8 &   &    {\bf Review} \\
 & & & & \quad    Study \S2.6-\S3.5 \\\cline{1-5}

27 & Thu & 9 &  & {\bf Examination \ex} \\
 & & & & \quad    \S2.6-\S3.5 \\\cline{1-5}

28 & Mon & 13 & \S3.10  &   Business and Economics Applications \\
 & & & & \quad     3-18 (divisible by 3)\\\cline{1-5}

29 & Tue & 14 & \S3.10  &   Business and Economics Applications \\
 & & & & \quad     30-34\\\cline{1-5}

30 & Wed & 15 & \S4.1  &   Antiderivatives \\
 & & & & \quad     3-48 (divisible by 3)\\\cline{1-5}

31 & Thu & 16 & \S4.2  &   Area, {\bf Quiz \qz} \\
 & & & & \quad     3-24 (divisible by 3)\\\cline{1-5}

   & Mon & 20 &  & {\bf Vacation} \\
& & & & \quad     3-24 Study \S1.1-4.2 \\\cline{1-5}

   & Tue & 21 &  & {\bf Vacation} \\
& & & & \quad     3-24 Study \S1.1-4.2 \\\cline{1-5}

32 & Wed & 22 & \S4.3  &   Riemann Sums \\
 & & & & \quad     3-21 (divisible by 3)\\\cline{1-5}

33 & Thu & 23 & \S4.3  &   Riemann Sums, {\bf Quiz \qz} \\
 & & & & \quad     25,26,43-48\\\cline{1-5}

\hline
\end{tabular}
\end{center}
\newpage
\begin{center}
\begin{tabular}{|l | l | l | l | l |}
\hline & {\bf Day} & {\bf Date} & {\bf Section} & {\bf Topic(s) and Homework} \\
\hline \hline
34 & Mon & 27 & \S4.4  &   The Fundamental Theorem of Calculus \\
 & & & & \quad     3-24 (divisible by 3)\\\cline{1-5}

35 & Tue & 28 & \S4.4  &   The Fundamental Theorem of Calculus \\
 & & & & \quad     27-42 (divisible by 3)\\\cline{1-5}

36 & Wed & 29 & \S4.5  &   Integration by Substitution \\
 & & & & \quad     3-27 (divisible by 3)\\\cline{1-5}

37 & Thu & 30 & \S4.6  &   Numerical Integration, {\bf Quiz \qz} \\
 & & & & \quad     1-5\\\cline{1-5}

38 & Mon & 3 Nov  & \S5.1  &   The Natural Logarithm Function and Differentiation \\
 & & & & \quad     3-6, 15-24 (divisible by 3), 42-54 (divisible by 3)\\\cline{1-5}

39 & Tue & 4 & \S5.2  &   The Natural Logarithm Function and Integration \\
 & & & & \quad     3-24 (divisible by 3)\\\cline{1-5}

40 & Wed & 5 &   &   {\bf Review} \\
 & & & & \quad     Study \S3.10-\S5.2  \\\cline{1-5}

41 & Thu & 6 &  & {\bf Examination \ex} \\
 & & & & \quad   \S3.10-\S5.2  \\\cline{1-5}

42 & Mon & 10 & \S5.3  &   Inverse Functions \\
 & & & & \quad     3-24 (divisible by 3)\\\cline{1-5}

43 & Tue & 11 & \S5.4  &   Exponential Functions \\
 & & & & \quad     19-22, 27-28, 30-42 (divisible by 3)\\\cline{1-5}

44 & Wed & 12 & \S5.5  &   Bases Other than $e$ and Applications \\
 & & & & \quad     3-36 (divisible by 3)\\\cline{1-5}

45 & Thu & 13 & \S5.6  &   Differential Equations: Growth and Decay, {\bf Quiz \qz} \\
 & & & & \quad     1-10\\\cline{1-5}

46 & Mon & 17 & \S5.7  &   Differential Equations: Separation of Variables \\
 & & & & \quad     3-24  (divisible by 3)\\\cline{1-5}

47 & Tue & 18 & \S5.8  &   Inverse Trigonometric Functions and Differentiation \\
 & & & & \quad      23-26,33-34,43-50\\\cline{1-5}

48 & Wed & 19 & \S5.9  &   Inverse Trigonometric Functions and Integration \\
 & & & & \quad     3-24  (divisible by 3)\\\cline{1-5}

49 & Thu & 20 & \S5.10  &   Hyperbolic Functions, {\bf Quiz \qz} \\
 & & & & \quad     7-12, 15-20, 37-40\\\cline{1-5}

50 & Mon & 24 & \S6.1  &   Area of a Region Between two Curves \\
 & & & & \quad      1-10\\\cline{1-5}

\hline
\end{tabular}
\end{center}
\newpage
\begin{center}
\begin{tabular}{|l | l | l | l | l |}
\hline & {\bf Day} & {\bf Date} & {\bf Section} & {\bf Topic(s) and Homework} \\
\hline \hline
51 & Tue & 25 & \S6.2  &   Volume: The Disk Method \\
 & & & & \quad     1-12\\\cline{1-5}

 & Wed & 26 &  & {\bf Vacation} \\
 & & & & \quad  Study \S1.1-\S6.2 \\\cline{1-5}

 & Thu & 27 &  & {\bf Vacation} \\
 & & & & \quad  Study \S1.1-\S6.2 \\\cline{1-5}

52 & Mon & 1 Dec & \S6.3  &   Volume: The Shell Method \\
 & & & & \quad     1-5\\\cline{1-5}

53 & Tue & 2 & \S6.3  &   Volume: The Shell Method \\
 & & & & \quad     6-10\\\cline{1-5}

54 & Wed & 3 Dec  &   &    {\bf Review} \\
 & & & & \quad    Study \S5.3-\S6.3 \\\cline{1-5}

55 & Thu & 4 &  & {\bf Examination \ex} \\
 & & & & \quad  \S5.3-\S6.3 \\\cline{1-5}

56 & Mon & 8 & \S6.4  &   Arc Length \\
 & & & & \quad     3-8 \\\cline{1-5}

57 & Tue & 9 & \S6.5  &   Work \\
 & & & & \quad    1-8\\\cline{1-5}

58 & Wed & 10 & \S6.6  &    Moments, Centers of Mass, and Centroids \\
 & & & & \quad    15-24  (divisible by 3)\\\cline{1-5}

59 & Thu & 11 & \S6.7  &   Fluid Pressure and Fluid Force \\
 & & & & \quad     1-18\\\cline{1-5}

\hline
 & Mon & 15 &  &{\bf Comprehensive Final Examination, }{\bf 13:00-15:00} \\
\hline
\end{tabular}
\end{center}

\vfill

\copyright 2006 Barton Willis
\end{document}
